% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Junwei Meng}

\basicInfo{
  \email{msql518@gmail.com} \textperiodcentered\ 
  \phone{(+86) 18710625606} \textperiodcentered\ 
  \github{github.com/maxluck518}
  }

\section{\faGraduationCap\ Education}

\datedsubsection{\textbf{Xi'an Jiaotong University} \hspace{0.5in} \textit{M.S, Computer Science and Technology}}{2016.9 -- Present}
\textit{My research focuses on the design of SDN data plane and FPGA development.} \
\datedsubsection{\textbf{Xi'an Jiaotong University} \hspace{0.5in} \textit{B.E, Computer Science and Technology）}}{2012.9 -- 2016.6} 
\textit{My research focuses on the improvement of the image scrambling encryption algorithm} \

\section{\faUsers\ Internship}
\datedsubsection{\textbf{Xilinx CTO Admin Research Lab in Singapore} }{2018.4 -- 2018.7}
Project: Programmable Packet Scheduling Strategy In Datacenter
\begin{onehalfspacing}
\begin{itemize}
\item{Designed queue scheduling IR and specified scheduling structure for dynamicly changing scheduling methods on different Network targets.}
\item{Designed a multi physical queue module and deployed it to the FPGA board (SmartNic or OnetSwitch) which can provide on-demand differentiated services for applications.}
\item{The system on the Kintex-UltraScale board can reach up to 25Gbps throughput in the experimental environment.}
\end{itemize}
\end{onehalfspacing}


\section{\faUsers\ Project Experience}

\datedsubsection{\textbf{Research for the deployment algorithm of CDN Network Server Nodes}}{2017.3 -- 2017.4}
\begin{itemize}
  \item Goals: Under the premise of satisfying all the consumer node, design a system which can automatically obtain the global optimal solution to setup the CDN server and the minimum total costs.
  \item Solution: Use heuristic algorithm and shortest path algorithm(spfa) by iteration to nearly achieve the optimal solution.
\end{itemize}

\datedsubsection{\textbf{PPPoE Enterprise Switch development} }{2017.3 -- 2017.8}
\begin{itemize}
  \item Developed the baseline procject of ONetSwitch 10g with SDNet.
  \item Designed a new dataplane for the service chain supporting PPPoE with P4 and implement the whole architecture on the ONetSwitch 10g.

\end{itemize}

\datedsubsection{\textbf{DFlow Switch Counter for Network Measurement}}{2017.9 -- 2017.11}
\begin{itemize}
  \item Designed the DFlow Counter module to cache and update the counter value with high-performance by reducing time solving hash conflict.
  \item Designed three-level hash table structure and Disco compression algorithm to save hardware resources.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item Skilled in: C/C++; Verilog, Vivado, HLS, SDX; Linux.
  \item Familiar with: Python; P4, Mininet; DPDK, Docker, Wireshark.
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\begin{itemize}[parsep=0.5ex]
  \item {CCF Software Capability Authentication, top20\% } \hfill  {2016}
  \item {Huawei Code Craft Competition'17 Silver Medal, top2\%} \hfill{2017.3 - 2017.4}
\end{itemize}

\section{\faInfo\ Miscellaneous}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item Language: English(CET-6)
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
